Effects on projectivity ratings by Embedding Operator and Trigger --- \newline Data Analysis

### 2022-11-23 materials-lisa/analysis/3_projection-across-operators/analysis.Rnw

>>>>

<<>>=
t = data_all %>% 
  mutate(verb = fct_relevel(verb, "suggest")) %>%
  mutate(op = fct_relevel(op, "q"))

#m.dummy = lm(projective ~ ai*short_trigger, data=t)
#summary(m.dummy)

# model with short_trigger slope did not converge
m.4 = lmer(projective ~ cai*short_trigger + (1+cai|content) + (1+cai|workerid), 
           data = t, REML=F,control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
saveRDS(m.4, "../models/m.4.rds")
m.4 <- readRDS("../models/m.4.rds")
summary(m.4)
texreg(m.4,single.row = TRUE, leading.zero = FALSE, booktabs = TRUE)
@
